---
title: "Group 04 Notebook"
output: html_notebook
authors: Hannah Ziegler, Tinashe Chingarande, Andrés Roa
---

R Studio Engine Room
```{r}
# Turn off scientific notation
options(scipen=999)

# Load the tidyverse.
library(tidyverse)
```
---
###MILESTONE 02###

Chosen paragraph:

“Beyond the mammoth cases, a pileup of other large payouts has padded the tab, a Times analysis of city payouts found. 

While the ##total number of payouts has dipped over time##, 

the ##average amount has increased.##

Last budget year, the city paid out 30 settlements of $1 million or more — five times as many as a decade before.”

--
Individual Data Points to ID:

- Payouts data
--
The Steps:

- Load the data

- Create a dataframe to deal only with the 2017 payouts
- Create a dataframe to deal only with the 2007-2017 payouts
- Find the number of payouts from each year
  - Sum the number (NOT THE TOTAL, ANDRES) of payouts per year
  - Find the percent change from 2007 to 2017
  
- Find average amount
  - Use the <mean> function to find that the average has increased
  
- Find the >= $1 million settlements   
  - Filter the 2017 payouts for settlements over $1 million, see how many there are
  - Filter the 2007 payouts for settlements over $1 million, see how many there are
 



```{r}
#Read in the data for 2006-2017 & read in the data for 2006-2017 TOTALS

```



